---
title: "Syllabus"
---


<a href="#" class="btn btn-default btn-lg btn-block">Block level button</a>


\section{Course Description} 
The main learning outcomes of this course are to get a broad idea about some frequently used probability models and to learn basic results and techniques in probability theory and statistical inference. Most of the materials for the course will be drawn from the first seven chapters of the textbook. The book does not, however, contain all the materials we intend to cover in this course. Some extra notes will therefore be given on those topics not in the text book. We will also introduce computational methods in statistics with the statistical software program \texttt{R}. 


```{r}
plot(mtcars$mpg)
```



```{r, results='asis'}
knitr::kable(mtcars)
```



<table class="table table-striped table-hover ">
  <thead>
    <tr>
      <th>#</th>
      <th>Column heading</th>
      <th>Column heading</th>
      <th>Column heading</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td>1</td>
      <td>Column content</td>
      <td>Column content</td>
      <td>Column content</td>
    </tr>
    <tr>
      <td>2</td>
      <td>Column content</td>
      <td>Column content</td>
      <td>Column content</td>
    </tr>
    <tr class="info">
      <td>3</td>
      <td>Column content</td>
      <td>Column content</td>
      <td>Column content</td>
    </tr>
    <tr class="success">
      <td>4</td>
      <td>Column content</td>
      <td>Column content</td>
      <td>Column content</td>
    </tr>
    <tr class="danger">
      <td>5</td>
      <td>Column content</td>
      <td>Column content</td>
      <td>Column content</td>
    </tr>
    <tr class="warning">
      <td>6</td>
      <td>Column content</td>
      <td>Column content</td>
      <td>Column content</td>
    </tr>
    <tr class="active">
      <td>7</td>
      <td>Column content</td>
      <td>Column content</td>
      <td>Column content</td>
    </tr>
  </tbody>
</table> 